TKT RNAseq: PNP analysis

### 2025-03-17 DeficiencyScreen/ManuscriptGOtermPlot.Rmd
updated files

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Candidate Suppressor Genes",
               marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0, xpad = 10),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3)))

>>>>

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Candidate Suppressor Genes",
               marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
               marker = list(colorscale = list(c(0,.9,1), c("#EA337F","#FEFF54", "#387EF7")),
               marker = list(colorscale = list(c(0,.9,1), c("#C1607E","#EBE3A4", "#419193")),
               marker = list(colorscale = list(c(0, .75, 1), c("#E7327F","#FEFE57", "#3A7EF7")),

    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0, xpad = 10),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3)))

### 2025-03-17 TKT_RNAseq/R Code/TKTRNAseqPNPAssessment.Rmd
updated files

add.edges = data.frame(enzyme = c("2.2.1.1",
                                  "5.1.3.1",
                                  "5.3.1.6",
                                  "5.4.2.7",
                                  "5.4.2.2"),
                       from = c("D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
                       to = c("D-sedoheptulose-7-phosphate",
                              "D-Xylulose 5-phosphate",
                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
                       arrows = c("to;from",
                                  "to;from",
                                  "to;from",
                                  "to;from",
                                  "to;from"),
                       FBgn = "")

@@

glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))

glycolysis.edges = data.frame(from = glycolysis.edges$from.name,
                              to = glycolysis.edges$to.name)
,
                              arrows = glycolysis.edges$arrow)
,
                              color = glycolysis.edges$color)
,
                              width = glycolysis.edges$size)
,
                              title = glycolysis.edges$title,
                              physics = T)

@@

node.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv", row.names = 1)
node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = node.colors
node.data[,'size'] = (node.data[,'size'] + 4.5)*7.5
node.colors[node.colors < (-2)] = -2
node.colors[node.colors>2] = 2
node.colors = (node.colors*100)+201
node.colors = setNames(temp[node.colors], names(node.colors)) 
node.data[names(node.colors), 'color.background'] = node.colors
node.data$title = paste0(node.data$id,
                         "<br>FC: ", node.data$FC,
                         "<br>pval: ", node.data$pval)
node.data[node.data$group == "Outside Path", 'color.background'] = 'black'
node.data[node.data$color.background == 'white', 'group'] = "no data"

@@

NAD.path = edges

@@

visedges = NAD.path
visedges$color = round(TKT.EdgeR.FC[NAD.path$FBgn, comparison.T],2)
##visedges$width = .5 + abs(visedges$color)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$color[is.na(visedges$color)] = "black"

@@

node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = node.colors
#node.data[names(node.colors),'size'] = 
#  (node.data[names(node.colors),'size'] + .5 + abs(min(node.colors)))*7.5
node.data[names(node.colors),'size'] = 
  (node.data[names(node.colors),'size'] + 3)*3.5

>>>>

#add.edges = data.frame(enzyme = c("2.2.1.1",
#                                  "5.1.3.1",
#                                  "5.3.1.6",
#                                  "5.4.2.7",
#                                  "5.4.2.2"),
#                       from = c("D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
#                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
#                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
#                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
#                       to = c("D-sedoheptulose-7-phosphate",
#                              "D-Xylulose 5-phosphate",
#                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
#                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
#                       arrows = c("to;from",
#                                  "to;from",
#                                 "to;from",
#                                "to;from",
#                                  "to;from"),
#                       FBgn = "")

@@

glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
                          "<br>log2(FC): ", 1,
                          "<br>FDR: ", 1,
                          "<br>", " cpm: ", 1,
                          "<br>", " cpm: ", 1)

glycolysis.edges = data.frame(from = glycolysis.edges$from.name,
                              to = glycolysis.edges$to.name,
                              arrows = glycolysis.edges$arrow,
                              color = glycolysis.edges$color,
                              width = glycolysis.edges$size,
                              title = glycolysis.edges$title,
                              physics = T)

@@

node.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv", row.names = 1)
node.names = unique(c(visedges$from, visedges$to))
node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = node.colors
node.data[,'size'] = (node.data[,'size'] + 4.5)*7.5
node.colors[node.colors < (-2)] = -2
node.colors[node.colors>2] = 2
node.colors = (node.colors*100)+201
node.colors = setNames(temp[node.colors], names(node.colors)) 
node.data[names(node.colors), 'color.background'] = node.colors
node.data$title = paste0(node.data$id,
                         "<br>FC: ", node.data$FC,
                         "<br>pval: ", node.data$pval)
node.data[node.data$group == "Outside Path", 'color.background'] = 'black'

node.data[node.data$color.background == 'white', 'group'] = "no data"

@@

NAD.path = edges
#write.csv(NAD.path, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/NAD.path.csv")

@@

visedges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/NAD.path.csv", row.names = 1)
visedges$color = round(TKT.EdgeR.FC[NAD.path$FBgn, comparison.T],2)
##visedges$width = .5 + abs(visedges$color)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$color[is.na(visedges$color)] = "black"

@@

node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = node.colors
#node.data[names(node.colors),'size'] = 
#  (node.data[names(node.colors),'size'] + .5 + abs(min(node.colors)))*7.5
node.data[names(node.colors),'size'] = 
  (abs(node.data[names(node.colors),'size']) + 3)*3.5
